Time stability in human interaction networks

### 2015-06-02 paper.tex
finished integration of n x m x gamma

In the scale of seconds and minutes, activity obeys a homogeneous pattern, with the messages being slightly more evenly distributed in all lists than in simulations using uniform distribution\footnote{Numpy version 1.6.1, ``random.randint'' function, was used for simulations, algorithms in \url{https://pypi.python.org/pypi/gmane}.}. In the networks, $\frac{max(incidence)}{min(incidence)} \in (1.26,1.275]$ while simulations reach these values but have in average more discrepant higher and lower peaks $\xi=\frac{max(incidence')}{min(incidence')} \Rightarrow \mu_\xi=1.2918 \text{ and } \sigma_\xi=0.04619$.
Therefore, the incidence of messages at each second of a minute and at each minute of an hour was considered uniform, i.e. no trend was detected. Circular dispersion is maximized and the mean has little meaning as indicated in Table~\ref{tab:circ}. As for the hours of the day, an abrupt peak appeared around 11am with the most active period being the afternoon. Days of the week revealed a decrease of at least one third and at most two thirds of activity on weekends. Days of the month were regarded as homogeneous with an inconclusive slight tendency of the first week being more active. Months of the year revealed patterns matching usual work and academic calendars. The time period examined here was not sufficient for the analysis of activity along the years. These patterns are exemplified in Tables~\ref{tab:hin}-\ref{tab:min2}.

@@

\FloatBarrier
\begin{table}
	\caption{Activity percentages along the days of the week for the four email lists. Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
	\begin{center}
		\begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
			\hline
			& Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
			\input{tables/tabWeekdays}
		\end{tabular}
	\end{center}
	\label{tab:win}
\end{table}

@@

With regard to the networks as the whole objects of analysis,
we were able to observe a negative correlation between the number of threads and the number of participants.
When the number of participants exceeds a threshold,
the number of threads displays a positive correlation with the number of participants.
This finding is illustrated with data from 140 email lists in the Figures~\ref{fig:nmgamma} and~\ref{fig:nmgamma3d} in the Supporting Information
and can also be observed in Table~\ref{tab:genLists}. Network types can be derived from such results, which is left for the reader and future work.

>>>>

@@

\begin{table}
	\caption{Activity percentages along the days of the week for the four email lists. Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.}
	\begin{center}
		\begin{tabular}{ | l |  c | c | c | c | c |   c | c |}
			\hline
			& Mon & Tue & Wed & Thu & Fri & Sat & Sun  \\ \hline
			\input{tables/tabWeekdays}
		\end{tabular}
	\end{center}
	\label{tab:win}
\end{table}
In the scale of seconds and minutes, activity obeys a homogeneous pattern, with the messages being slightly more evenly distributed in all lists than in simulations using uniform distribution\footnote{Numpy version 1.6.1, ``random.randint'' function, was used for simulations, algorithms in \url{https://pypi.python.org/pypi/gmane}.}. In the networks, $\frac{max(incidence)}{min(incidence)} \in (1.26,1.275]$ while simulations reach these values but have in average more discrepant higher and lower peaks $\xi=\frac{max(incidence')}{min(incidence')} \Rightarrow \mu_\xi=1.2918 \text{ and } \sigma_\xi=0.04619$.
Therefore, the incidence of messages at each second of a minute and at each minute of an hour was considered uniform, i.e. no trend was detected. Circular dispersion is maximized and the mean has little meaning as indicated in Table~\ref{tab:circ}. As for the hours of the day, an abrupt peak appeared around 11am with the most active period being the afternoon. Days of the week revealed a decrease of at least one third and at most two thirds of activity on weekends. Days of the month were regarded as homogeneous with an inconclusive slight tendency of the first week being more active. Months of the year revealed patterns matching usual work and academic calendars. The time period examined here was not sufficient for the analysis of activity along the years. These patterns are exemplified in Tables~\ref{tab:hin}-\ref{tab:min2}.

\FloatBarrier

@@

With regard to the networks as the whole objects of analysis,
we were able to observe a negative correlation between the number of threads and the number of participants.
When the number of participants exceeds a threshold,
the number of threads displays a positive correlation with the number of participants.
This finding is illustrated in Figure~\ref{fig:nmgamma3d} and can also be observed in Table~\ref{tab:genLists}.
Network types can be derived from such results, which is left for the reader and future work.

\begin{figure}
   \centering
        \includegraphics[width=\columnwidth]{figs/mpgamma____}
	\caption{A 3D scatter plot of messages (M) versus participants (N) versus threads ($\Gamma$) 140 email lists. The highest number of threads are found in lists with few participants. The correlation between $N$ and $\Gamma$ is negative for low values of $N$ but positive otherwise.}
	\label{fig:nmgamma3d}
\end{figure}
